\SW: I. Crowd-sourcing the Discovery of Gravitational Lenses

### 2015-05-14 doc/sw-system.tex
Closes #211

We describe \SW, a novel gravitational lens discovery service that yields
samples of high purity and completeness through crowd-sourced visual inspection.
Carefully produced colour composite images are displayed to volunteers via a
web-based classification interface, which records their estimates of the positions of
candidate lensed features. Simulated lenses, and expert-classified images which
lack lenses, are inserted into the image stream at random intervals; this
training set is used to give the volunteers instantaneous feedback on their performance, as
well as to calibrate a model of the system that provides
dynamical updates to the probability that a classified image contains a lens. Low probability systems are
retired from the site periodically, concentrating the sample towards a set of lens
candidates. Having divided 160 square degrees of Canada-France-Hawaii Telescope
Legacy Survey (\cfhtls) imaging into some 430,000 overlapping 82 by 82 arcsecond
tiles and displaying them on the site, we were joined by around 37,000
volunteers who contributed 11~million image classifications over the course of 8
months. This \StageOne search reduced the sample to 3381 images containing candidates; these were then
refined in \StageTwo to yield a sample that we expect to be over 90\% complete and 30\% pure, based on our analysis of the volunteers performance on training images (refer for \Sref{sec:design:stages} for more information on the two stage strategy) .
We comment on the scalability of the \SW system to the wide field survey era,
based on our finding that searches of $10^5$ images can be performed by a
crowd of $10^5$ volunteers in 6 days.
\end{abstract}

>>>>

We describe \SW, a novel gravitational lens discovery service that yields
samples of high purity and completeness through crowd-sourced visual inspection.
Carefully produced colour composite images are displayed to volunteers via a
web-based classification interface, which records their estimates of the
positions of candidate lensed features. Simulated lenses, and expert-classified
images which lack lenses, are inserted into the image stream at random
intervals; this training set is used to give the volunteers instantaneous
feedback on their performance, as well as to calibrate a model of the system
that provides dynamical updates to the probability that a classified image
contains a lens. Low probability systems are retired from the site periodically,
concentrating the sample towards a set of lens candidates. Having divided 160
square degrees of Canada-France-Hawaii Telescope Legacy Survey (\cfhtls) imaging
into some 430,000 overlapping 82 by 82 arcsecond tiles and displaying them on
the site, we were joined by around 37,000 volunteers who contributed 11~million
image classifications over the course of 8 months. This \StageOne search reduced
the sample to 3381 images containing candidates; these were then refined in
\StageTwo to yield a sample that we expect to be over 90\% complete and 30\%
pure, based on our analysis of the volunteers performance on training images.
We comment on the scalability of the \SW system to the wide field
survey era, based on our projection that searches of $10^5$ images could be performed
by a crowd of $10^5$ volunteers in 6 days.

\end{abstract}
